\documentclass[9pt]{extarticle} % {8 ... 12, 14, 17, 20}pt (adjust to fit one page)

\usepackage[letter, margin=0.5in]{geometry}
\usepackage{emuserutils}

\setBulletStyle{$\circ$}

% Adjust spacings to fit one page
\setBulletsSpacing{0.1 \baselineskip}  % [0.1 ... 0.5] (recommended)
\setSectionSpacing{0.3 \baselineskip}  % [0.3 ... 0.7] (recommended)

\begin{document}

\lrHeader
{First Last}
{(012) 345-6789 \textbf{
        $\vert$ \href{mailto:myprofessional@email.com}{myprofessional@email.com}
        $\vert$ \href{https://www.linkedin.com/in/firstlast/}{LinkedIn}
        $\vert$ \href{https://www.youtube.com/watch?v=dQw4w9WgXcQ}{firstlast.com}}}

\begin{sectionList}{Education}
    \item \lr
    {Two Degrees University}{City, ST}
    [D.M.A in Resumes $\vert$ GPA: 0.00/4.00][Month Year -- Month Year]
    [B.M. in Something, Minor in Something Else][Dec. 2048]
    \begin{nobullets}
        \item \labeled
        {Coursework}{Can move this section below \textsc{Experience/Projects} (usually when experience $>$ education)}
        \item \labeled
        {Extracurriculars \& Honors}{Delete this entire \texttt{nobullets} list if it's not worth the space}
    \end{nobullets}
\end{sectionList}

\begin{sectionList}{Experience}
    \item \lr
    {EmployMePlease}{City, ST}
    [CEO Intern][Jan. 0000 -- Present]
    \begin{bullets}
        \item Optimized a customized system for job hunting to be 69\% faster though automated tools, enabling myself to apply to 9000+ positions across 51 states in the U.S. while setting new personal-best records of career desperation
        \item Boosted recruiter response rates by $\times \infty$ by using the \href{https://www.inc.com/bill-murphy-jr/google-recruiters-say-these-5-resume-tips-including-x-y-z-formula-will-improve-your-odds-of-getting-hired-at-google.html}{X-Y-Z format} and not over-bolding technical skills such as \textbf{Microsoft Office, Google Suite, and ChatGPT}
    \end{bullets}

    \item \lr
    {University of Illinois Chambana-Urpaign}{\textnormal{Dates can go here instead!}}
    [Teaching Unassistant][]
    \begin{bullets}
        \item There are many ways to use \texttt{lr}: omit the location, move the dates, etc. \textbf{(just be consistent)}
    \end{bullets}

    \item \lcr
    {Left Company}{Center Position}{Right Dates}
    \begin{bullets}
        \item Or maybe you like \texttt{lcr} \textbf{(just be consistent)}
    \end{bullets}

    \item \lr
    {Syntax Inc. $|$ \textnormal{\textit{Senior Hardware and Software Research Development Engineering Manager}}}{ca. 420 BCE -- 0 CE}
    \begin{bullets}
        \item Play around with \href{https://www.overleaf.com/learn/latex/Font_sizes%2C_families%2C_and_styles}{font sizes, families, and styles} \textbf{(just be consistent)}
        \item Can use periods \textbf{(just be consistent)}.
        \item Beware: `|' is different from `$\vert$'!
    \end{bullets}
\end{sectionList}

\begin{sectionList}{Title}
    \item \lr{Item 1}{}
    \item \lr{Item 2}{}
    \item  \lr{Company}{Location}
    [Position][Dates]
    \item \lr{University}{}  % Omits location
    [Degree 2][Dates]
    [Degree 1][Dates]
    \item \lr{Project}{Dates}  % Right-column is non-italicized if there are only two values
    \item \lcr{Left}{Center}{Right}
\end{sectionList}

\begin{sectionList}{Projects}
    \item \lr
    {\href{https://github.com/quinnouyang/emuser}{Emuser}: A Pretty Awful Resume Template}{Dec. 2023 -- Present}
    \begin{bullets}
        \item Released a modern LaTeX resume template used by at least 1 hooman, introducing accessible formatting options, standardizing multi-line section items, and virtually eliminating vertical spacing hacks
        \begin{bullets}[$\bullet$]
            \item Think twice before nesting bullets (can look messy).
            \item[$\sharp$] You can customize them though!
        \end{bullets}
    \end{bullets}

    \item \lr
    {No Spelling Mistakes Here!}{January 2023 -- Janurary 2023}
    \begin{nobullets}
        \item Since I only have one thing to say, maybe I don't want bullet points...
    \end{nobullets}
\end{sectionList}

\begin{sectionList}{Skills \& Interests}
    \item \begin{nobullets}
        \item \labeled
        {Programming Languages}{HTML}
        \item \labeled
        {Symbols to Escape}{\&, \%, \$, \#, etc.}
        \item \labeled
        {Interests}{Pay trasparency laws, Sesame the cat, \textit{Law \& Order}}
    \end{nobullets}
\end{sectionList}

\dateFooter

\end{document}